### 2016-04-11 extended-abstract.tex
fix typos and expositional awkwarness in extended abstract

This question can be addressed in the context of renewals of trade remedies under the WTO agreements. Normally, temporary measures such as anti-dumping and counter-vailing duties are imposed with a five-year sunset provision that is subject to renewal by the U.S. International Trade Commission. Conditional on a TTB being granted and applied for five years, one would like to know what determines whether a renewal order is granted so that it continues in force. \\

@@

In this model, there are two phases of interaction between any given industry seeking protection and the ITC. In both cases, all the actors take most-favored-nation (MFN) tariffs as given. \\

@@

An industry's decision about how much, if any, effort to exert depends on a number of factors. Among them are the gap between the applied tariff it faces and the protection it would receive under a TTB, the cost of seeking the TTB, and, crucially, the probability that its request will be granted. That it, the industry's incentives to seek protection, and the intensity with which it does so, depend on how much uncertainty it faces in the ITC's decision-making process. \\

@@

There are several possible sources of this uncertainty. The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a TTB. Indirectly, this may reflect the ITC's preferences about the costs of disputes and retaliation by trade partners. Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to consumers and trading relations. This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question. \\

@@

Because a TTB insulates an industry from competition, when receiving such protection, and industry should be able to increase profits. The amount that profits increase will vary by industry, and the decisions about how to use the extra profits will also plausibly vary. Some industries may use this opportunity to become more competitive and thus less interested in seeking protection while others may use the added profits to become more politically powerful and thus better able to gain future protection. These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the ITC. \\

>>>>

This question can be addressed in the context of renewals of trade remedies under the WTO agreements. Normally, temporary measures such as anti-dumping and counter-vailing duties are imposed with a five-year sunset provision that is subject to renewal by the U.S. International Trade Commission. Conditional on a TTB being granted and applied for five years, one would like to know what determines whether a renewal order is granted so that the measure continues in force. \\

@@

In this model, there are two phases of interaction between any given industry seeking protection and the ITC. In both cases, I assume that all actors take most-favored-nation (MFN) tariffs as given. \\

@@

An industry's decision about how much, if any, effort to exert depends on a number of factors. Among them are the gap between the applied tariff it faces and the protection it would receive under a TTB, the cost of seeking the TTB, and, crucially, the probability that its request will be granted. That is, the industry's incentives to seek protection, and the intensity with which it does so, depend on how much uncertainty it faces in the ITC's decision-making process. \\

@@

There are several possible sources of this uncertainty. The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a TTB. Indirectly, this may reflect the ITC's preferences about the costs of disputes and retaliation by trade partners. Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to up- and down-stream industries, consumers and trading relations. This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question. \\

@@

Because a TTB insulates an industry from competition, when receiving such protection, an industry should be able to increase profits. The amount that profits increase will vary by industry, and the decisions about how to use the extra profits will also plausibly vary. Some industries may use this opportunity to become more competitive and thus less interested in seeking protection while others may use the added profits to become more politically powerful and thus better able to gain future protection. These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the ITC. \\
